---
title: microclimloggers
output:
  md_document:
    variant: markdown_github
---

```{r chunk_opts, echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.path = "inst/img/",
  cache.path = "inst/cache/"
)
```

[![R](https://github.com/RyanLab/microclimloggers/actions/workflows/r.yml/badge.svg)](https://github.com/RyanLab/microclimloggers/actions/workflows/r.yml)

`microclimloggers`: Data Wrangling Functions For Microclimate Loggers

An R package to process various microclimate logger data formats. Functions are provided to parse and reshape microclimate logger data (e.g. iButton, iButton Hygrochron, HOBO pendant loggers [temperature, humidity, light]) that are commonly used in the environmental and biological sciences.

## Installation

Install `microclimloggers` from GitHub:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("RyanLab/microclimloggers")
```

## Examples

Load `microclimloggers` package:
```{r}
library("microclimloggers")
```

Get the path of an example file (HOBO RH Logger)
```{r}
hobo_example_path <- system.file("extdata", "HOBO_RH_logger.csv", package = "microclimloggers")
```

Parse the file
```{r}
hobo_data <- read_hobo_csv(hobo_example_path)
```

Plot the file
```{r}
plot(hobo_data)
```

The `read_hobo_csv` function has additional features. It flexibly handles any combination of temperature, humidity, and light.
```{r}
# logger deployed at ground level over winter to measure snowmelt date
templight_path <- system.file("extdata", "HOBO_LIGHT_logger.csv", package = "microclimloggers")
templight_data <- read_hobo_csv(templight_path)
plot(templight_data)  # snow melted in late April
```

It also reports the units of measurement...
```{r}
templight_data$df_units
```

...and allows for conversion between measurement systems during data import.
```{r}
templight_imperl <- read_hobo_csv(templight_path, units_out = "imperial")
plot(templight_imperl)
```

All other functions assume that metric units are used.

## Meta

* Please [report any issues or bugs](https://github.com/pboesu/microclimloggers/issues).
* License: GPL-3
* Get citation information for `microclimloggers` in R doing `citation(package = 'microclimloggers')`

##Funding

* This work was supported by funding from [NSF grant DEB-1641145](https://nsf.gov/awardsearch/showAward?AWD_ID=1641145) and [NSF grant DEB-1518681](https://nsf.gov/awardsearch/showAward?AWD_ID=1518681)


